Investigating magnetic dynamo evolution with TESS field dwarfs

### 2017-10-04 ms.tex
adding some citations

In addition, we will use the rotation periods of comoving stars identified in
the first \Gaia\ data release \citep{oh2017} to quantify the accuracy and
precision of gyrochronology.
We have identified 38 stars in 19 pairs with \Gaia\ proper motions and radial
velocities from \RAVE\ that are observable by \TESS, using {\tt tvguide}.
Of these, 34 stars in 17 pairs are already in the CTL list.
Because the stars in these pairs are assumed to be recently disrupted
binaries, we expect them to have the same age and measuring their rotation
periods will therefore allow us to test gyrochronology.

Finally, we hope to use the improved gyrochronology relations, calibrated
using \TESS\ data to infer the dependence of planet frequency on age and
position in the galaxy.
\kepler\ revealed tantalizing hints that exoplanets on short orbital periods
have larger radii and are more infrequent around young stars \citep{mann2016a,
mann2016b, rizzuto2017}.
Do these trends continue into older ages and do they exist in the field?
We will answer these questions by inferring ages for \TESS\ field stars.

>>>>

In addition, we will use the rotation periods of comoving stars identified in
the first \Gaia\ data release \citep{oh2016} to quantify the accuracy and
precision of gyrochronology.
We have identified 38 stars in 19 pairs with \Gaia\ proper motions and radial
velocities from \RAVE\ that are observable by \TESS, using {\tt tvguide}.
Of these, 34 stars in 17 pairs are already in the CTL list.
Because the stars in these pairs are assumed to be recently disrupted
binaries, we expect them to have the same age and measuring their rotation
periods will therefore allow us to test gyrochronology.

Finally, we hope to use the improved gyrochronology relations, calibrated
using \TESS\ data to infer the dependence of planet frequency on age and
position in the galaxy.
\kepler\ revealed tantalizing hints that exoplanets on short orbital periods
have larger radii and are more infrequent around young stars \citep{mann2017a,
mann2017b, rizzuto2017}.
Do these trends continue into older ages and do they exist in the field?
We will answer these questions by inferring ages for \TESS\ field stars.
